{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-06-09 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

\chapter{Advanced Enhancement Techniques in Accelerated Proximal Gradient}
    We review advanced enhancement techniques in Accelerated Proximal Gradient method. 
    The review will be based on several papers. 
    \par
    There are several notable enhancements of the FISTA for function that are not strongly convex. 
    Monotone variants of FISTA proposed by Beck \cite{beck_fast_2009-1} and Nesterov \cite[2.2.32]{nesterov_lectures_2018} imposes monotonicity in function value at the iterates.  
    Backtracking strategies from Chambolle \cite{calatroni_backtracking_2019} shows that the underestimating Lipschitz constant using a backtracking technique to choose a next iterate improves the average runtime of the algorithm in practice. 
    They showed that the convergence rate is bounded by the estimates of the Lipschitz constant. 
    Restart is a technique discussed in Necoara et al. \cite{necoara_linear_2019}.
    They showed that there exists an optimal restarting interval to achieve fast linear convergence rate for all functions with quadratic growth condition. 
    The method of restarting was improved to be parameter free while still retaining a fast linear convergence rate, see Alamo et al. \cite{alamo_restart_2019} and Aujol et al. \cite{aujol_parameter-free_2024}. 
    \par
    In this chapter, we will go through the details of these enhancements of FISTA and discuss why they are important in theories, and in practice.

>>>>

\chapter{Advanced Enhancement Techniques in Accelerated Proximal Gradient}
    This chapter is the draft for an upcoming paper. 
    The writing style will change to fit this purpose better. 
    \par
    There are several notable enhancements of the FISTA for function that are not strongly convex. 
    Monotone variants are proposed by Beck \cite{beck_fast_2009-1} and Nesterov \cite[2.2.32]{nesterov_lectures_2018}. 
    Chambolle proposed the Backtracking strategy \cite{calatroni_backtracking_2019}.
    Restart is a technique can be found in Necoara et al. \cite{necoara_linear_2019}, \cite{alamo_restart_2019} and Aujol et al. \cite{aujol_parameter-free_2024}.
